Robust Quantum Optimal Control

### 2020-07-21 paper/paper.tex
progress

\documentclass[
  amsfonts,
  amsmath,
  tbtags,
  amssymb,
  aps,
  nobibnotes,
  prl,
  twocolumn,
]{revtex4-2}

@@

Some analytical methods
have been presented to address realistic experimental constraints.
Considering the dynamical and geometric phases of state
evolution has led to methods for achieving
robustness to pure dephasing in quantum systems
\cite{xu2020nonadiabitc, han2020experimental, merrill2014progress}.
Additionally, suitable choices of bases have been demonstrated that
allow the experimentalist to infer tradeoffs in longitudinal
and pure dephasing coherence times \cite{huang2020engineering}.
To date, however, no analytical method has been presented
to construct a gate while satisfying all relevant experimental
constraints. Furthermore, most analytic methods have only
been demonstrated in the two-level approximation and become
cumbersome to solve for larger Hilbert space sizes.

@@

(This work) We employ the trajectory optimization
literature to formulate the quantum
optimal control problem as a constrained optimization problem.
The trajectory optimization framework allows us to handle arbitrary
constraints on the evolution of the quantum state. Additionally,
we introduce methods for constructing gates robust to longitudinal
relaxation and pure dephasing, the dominant barrier to experimentally
realizing practical quantum computing.

We study the quantum optimal control problem on the fluxonium qubit.
We outline experimentally realistic constraints and map them to
the trajectory optimization framework. For the device we study
we achieve a 1.5x increase in $T_{1}$ times.
We present two methods for achieving robustness to pure dephasing,
and compare them to existing dynamic decoupling methods. We find that 
our methods mitigate dephasing by order X over dynamic decoupling.

@@

%% SECTION 2
\section{QOC + AL-iLQR}
(QOC Problem Statement) Here we introduce the notation
we will use throughout the paper,
review the quantum optimal control problem statement,
and introduce the trajectory optimization framework.
Quantum optimal control concerns the evolution of
a quantum state $\ket{\psi(t)}$ governed by the time-dependent
Schroedinger equation (TDSE)
\begin{align}
  \frac{d}{dt} \ket{\psi(t)} &= -\frac{i}{\hbar} H(\textbf{u}(t), t) \ket{\psi(t)}
\end{align}
The evolution is sometimes cast with the evolution
of a density matrix under the Lindblad master equation to
model the decoherence of the state explicitly. The Hamiltonian
depends arbitrarily on the controls ($\textbf{u}(t)$). The controls
are so called because they are the means the experimentalist has to
act on the system.

Numerical quantum optimal control techniques make
the problem tractable by discretizing the problem into $N$
time steps. Typical integration techniques for the TDSE include
approximating unitary propagators as well as explicit integration methods,
such as Runge-Kutta, of the form
\label{step-approx}
\begin{align}
  \ket{\psi_{k + 1}} \approx \ket{\psi_{k}} + \frac{d}{dt} \ket{\psi_{k}} \cdot \Delta t_{k}
\end{align}

Quantum optimal control seeks the control
parameters that minimize a functional $J(\textbf{u}(t))$.
In the simplest case the functional is
$J = 1 - {\lvert \braket{\psi_{f} \lvert \psi_{N}(\textbf{u}(t))} \rvert}^{2}$
the infidelity between the inital state evolved
to the final time step ($\ket{\psi_{N}(\textbf{u}(t))}$)
and the target state ($\ket{\psi_{f}}$). In general
$J$ is a linear combinaion of cost functions on the state, e.g.
forbidden-state occupation, as well as
cost functions on the controls, e.g. the norm of the control amplitudes
\cite{leung2017speedup}. Typical quantum optimal control
algorithms employ automatic differentiation
to compute first order information for the functional ($\nabla_{u} J(u)$).
They employ a first-order optimizer to minimize $J$ with respect to $u$.

(AL-iLQR Problem Statement) The trajectory optimization
literature solves a more general class of non-linear programs that resemble
the quantum optimal control problem. The quantum optimal control
problem is a specific case of the linear quadratic regulator (LQR).
LQR is so called because the dynamics are linear in the state and
the functional is quadratic in the state. In the LQR formulation
the same functional is evaluated at each time step
\begin{equation}
  J_{\textrm{iLQR}} = \tilde{x}_{N}^{T} Q_{N} \tilde{x}_{N}
  + \sum_{k = 0}^{N - 1} \tilde{x}_{k}^{T} Q_{k} \tilde{x}_{k} + u_{k}^{T} R_{k} u_{k}
\end{equation}
where $\tilde{x}_{k} = x_{k} - x_{f}$ is the difference between the state
at time step $k$ and final state, $u_{k}$ are the controls,
and $Q_{k}, R_{k}$ are matrices that define the penalty metric.
The state is propagated using a dynamics function similar to \ref{step-approx}
$x_{k + 1} = f(x_{k}, u_{k}, t_{k}, \Delta t_{k})$.
In the case of quantum optimal control $\ket{\psi_{k}} \subseteq x_{k}$
and $f$ encodes the TDSE dynamics.

@@

%% SECTION 3
\section{QOC on the Fluxonium}
(Fluxonium Device) In the following we study
the quantum optimal control problem on the fluxonium qubit.
In the two-level
approximation the system Hamiltonian takes the form
\label{hamiltonian}
\begin{align}
  H/h &= \omega_{q} \frac{\sigma_{z}}{2} + u(t) \frac{\sigma_{x}}{2}
\end{align}
$h$ is Planck's constant. The control parameter $u$ is experimentally
realized by modulating the flux 
threading the superconducting junction $\Phi_{\textrm{ext}}$.
The conversion is defined by
$u = 4 \pi \braket{g \lvert \hat{\phi} \rvert e} E_{L} \delta \Phi_{\textrm{ext}} / \Phi_{0}$
where $\delta \Phi_{\textrm{ext}} = \Phi_{\textrm{ext}} - 0.5 \Phi_{0}$ is the flux
offset from the flux frustration point.

@@

(Constraints) We now outline the constraints that we require each gate
to obey.
We require $u(t = 0) = u(t = t_{N}) = 0$.
This constraint ensures gates may be concatenated arbitrarily without
inducing AWG ringing due to high-frequency transitions.
Furthermore, we require $\int_{0}^{t_{N}} u(t) dt = 0$. This
constraint ensures the pulse has zero net flux, mitigating
the hysteresis ubiquitous in flux bias lines.
%% TODO: See ref. 28 in Helin paper
We require $-300 \textrm{MHz} \le u(t) \le 300 \textrm{MHz}$
to ensure the two-level approximation \ref{hamiltonian}
remains valid. Additionally, we require that each gate achieves
the desired state transition $\braket{\psi_{f} \lvert \psi_{N}} = 1$.
In addition to these constraints we penalize the norm
of the first and second derivatives of the control
to mitigate AWG ringing.

The equality and inequality constraints on $u$ are handled
with a bound constraint. $\int_{0}^{t_{k}} u(t) dt$ is added
to the augmented state vector $x_{k}$ by incorporating the
integration of $u_{k}$ into the dynamics function $f$.
Both the zero net flux and target quantum state constraint
are then handled by ensuring the augmented final state is
reached $x_{N} - x_{f} = 0$. The optimization is performed
over the second derivative of the controls $\frac{d^{2}}{dt^{2}} u(t)$
so that the second derivative, first derivative, zeroth derivative, and
integral of the controls may be penalized.
%% TODO: probably want to list equations for the constraints

($T_{1}$ and $T_{\phi}$ noise)
In addition to optimizing the cost functional to achieve a gate
that obeys experimental constraints and has a high simulated fidelity,
we also want to make the gate robust to noise that affects the experimental
fidelity of the gate. Decoherence of the quantum state due to external noise
is typically modeled by two phenomena: longitudinal relaxation and pure dephasing.
They are modeled using their $1/e$ decay times $T_{1}$ and $T_{\phi}$ respectively
(see Appendix).
The main contributions to longitudinal relaxation in our
device are dielectric loss in the capacitor, resistive loss in the inductor,
and Purcell loss. The main contributions to pure dephasing in our
device are $1/f$ flux noise and decay via charge and flux coupling
to the control lines.

Dissipation to the thermal bath via longitudinal
relaxation is an irreversible process
that results in information loss.
Converesely, pure dephasing is a reversible process.
There is a tradeoff between the two decoherence processes. In the case of white
noise we have that the sum of the noise weights $W_{1}$ and $W_{\phi}$
is constant \cite{huang2020engineering}.
Our device achieves its best pure dephasing
protection at the flux frustration point
$T_{2e}(\Phi_{\textrm{ext}} = 0.5 \Phi_{0}) \sim 300 \mu\textrm{s}$
where the qubit frequency is first-order insensitive to changes in flux.
It becomes more succeptable to pure dephasing as the flux is tuned away from the flux
frustration point. Conversely, $T_{1}$ is at a minimum
around the flux frustration point $T_{1}(0.5 \Phi_{0}) = 0.315$ms,
and increases away from the flux frustration point
$T_{1}(0.43 \Phi_{0}) = 4.3$ms. Given the nature
of the decay processes and the tradeoff, we choose
to maximize the longitudinal relaxation time ($T_{1}$)
over the gate duration
and employ robust control techniques to mitigate
pure dephasing.
%% TODO: See fig. 3 in Helin paper

%% LOH
%% SECTION 4
\section{Robustness to $T_{1}$-type Noise}
(Strategy) We seek to minimize the probability
that the qubit relaxes longitudinally.
To this end we augment the state vector $x_{k}$ with the
longitudinal relaxation probability
\begin{align}
  P_{1}(t_{k}) = \int_{0}^{t_{k}}
  \gamma_{1}(\Phi_{\textrm{ext}}(t)) dt
\end{align}
where $\gamma_{1} = T_{1}^{-1}$. Setting the target
longitudinal relaxation probability to 0 results in
a quadratic cost at each knot point
of the form ${\lvert P_{1}(t_{k}) \rvert}^{2}$.

The value $T_{1}(\Phi_{\textrm{ext}}(t_{k}))$
is obtained at each knot point by evaluating
a spline interpolant fit to
experimentally obtained data of the form
$\{(\Phi_{\textrm{ext}}, T_{1})\}$.
Calculating $T_{1}$ directly from theoretical
considerations requires many high-dimensional
eigendecompositions, which
is computationally expensive. Additionally,
$T_{1}$ values are known to fluctuate greatly
with laboratory temperatures \cite{klimov2018fluctuations}.
Interpolating $T_{1}$ from experimental data increases
the fridge truth of the simulation.

@@

(Results) We achieve a factor of 1.5 decrease in the probability
of longitudinal relaxation from the analytic gates we benchmark
against. We simulate the performance of the gates using the
lindblad master equation (see Appendix X). We repeatedly apply the basis gates
and measure the fidelity of the resulting state as a function
of time as shown in Fig. 1.

%% T4.1
%% TODO: Update this table with spline T1 optimizations and calculations.
%% TODO: Maybe best for appendix.
%% TOOD: Maybe add some commentary about why we see more speedup
%% for Z/2 and X/2 than Y/2. In particular I think this is because of the
%% long idle times at the flux frustration point for Z/2 and X/2. It
%% might be a more fair comparison to show gates that have better T1s
%% and as good flux noise mitigation.
\begin{table}
  \begin{tabular}{c | c | c | c}
    & Analytic  & QOC &\\
    Gate & $P_{1}\ (10^{-5})$ & $P_{1}\ (10^{-5})$ & Speedup\\
    \hline
    Z/2 & 4.615 & 2.576 & 1.792\\
    Y/2 & 2.826 & 1.888 & 1.496\\
    X/2 & 9.562 & 5.080 & 1.882\\
  \end{tabular}
  \caption{Probability of longitudinal relaxation for each gate
    evaluated at the gate's duration.}
\end{table}

%% F4.1
%% TODO: Update images. Use new gates constructed with
%% spline T1 and use smaller sim times.
\begin{figure}[ht]
  \begin{subfigure}{.33\textwidth}
    %% \includegraphics[width=\linewidth]{assets/00045_spin16.png}
    \label{fig:sub-first}
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    %% \includegraphics[width=\linewidth]{assets/00047_spin16.png}
    \label{fig:sub-second}
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    %% \includegraphics[width=\linewidth]{assets/00049_spin16.png}
    \label{fig:sub-third}
  \end{subfigure}
  \caption{Master equation simulation with $T_{1}$ dissipation for all basis gates.}
  \label{fig:fig}
\end{figure}

%% SECTION 5
\section{Robustness to $T_{\phi}$-type Noise}
(Strategy) System parameter deviations arise due to
measurement error and noise injection. For example,
we might measure $\omega_{q}$ inaccurately,
which leads to a deviation from
the the drive frequency $\omega_{d}$.
Further, we may have some temperature dependent gain
in the lines leading to the device, or 1/$f$ noise
and $A(\Phi_{\textrm{ext}})$ comes out with some
$\delta A$ on the flux axis.
Both of these effects lead to dephasing,
uncertain dynamics, and thus erroneous computation.

These problems are typically attacked with dynamic decoupling
sequence where an erroneous rotation is compensated for with
one that cancels the $\delta$. However, we can do better
than the first order variants of these pulses.

We propose two methods for engineering robustness
to system parameter deviations. The first we call the
derivative method. We use the intuition that
making the final state insensitive to changes
in the system parameter is encoded in the derivative
$\partial_{\omega}^{l} \ket{\psi_{N}}$.
In particular, we find that going to the second
derivative is good. The first derivative is already
small, especially for the $\delta A$ time, because,
near the end of optimization, the
optimizer is unable to improve the final state by
changing the flux bias.
The dynamics for propgating the derivative of the state
are found by differentiating the schroedinger equation
dynamics with respect to the parameter of interest.
The scheme boils down to propagating sequential
derivatives of the parameter you want to be
robust to $\partial_{\omega}^{l}$ and penalizing thier norm
${\lvert \partial_{\omega}^{l} \lvert}^{2}$.

The other scheme we call the sampling method. This method
is well-known in the trajectory optimiztion. In this scheme
we propgate an array of states whose dynamics differ
in that the parameter of interest is altered slightly
for each state. In the 3-point sampling method we
propagate $\psi_{\pm}$, $\psi$ where
$\omega_{\pm} = \omega \pm \delta \omega$. Here $\delta$ is
typically taken at standard deviations of the parameter
of interest.

@@

%% F5.1
%% TODO: Update this and make sure it is for X/2.
%% I'm not sure if we should include all gates Z/2, Y/2, X/2
%% because I don't know what the dynamic decoupling analogy
%% for Z/2 and Y/2 are. On the other hand we would
%% want to include all of them to show that the benefit
%% is not uniform across gates.
\begin{figure}
  %% \includegraphics[width=\linewidth]{assets/00005_spin12_hpsweep.png}
  \caption{fidelity v.s. $\omega$ for the $X/2$ gate via
    analytic, 3-sample, 2-derivative (maybe add 5-sample and 3-derivative)}
\end{figure}

%% F5.2
%% TODO: Update this and make sure it is for X/2.
%% Add inset to show high-performing variants at large time steps.
\begin{figure}
  %% \includegraphics[width=\linewidth]{assets/00006_spin12_hpsweep.png}
  \caption{fidelity at $\omega \pm \sigma_{\omega}$ v.s. time for the
    $X/2$ gate via analytic, 3-sample, 2-derivative
    (maybe add 5-sample and 3-derivative)}
\end{figure}

%% F5.3
%% TODO: Make this figure. My guess is we want a 5-sample, with 2 at \omega_{\pm}
%% and 2 at A_{\pm} as well as 2-derivative of both parameters separately.
\begin{figure}
  %% \includegraphics[width=\linewidth]{assets/t2_temp.jpg}
  \caption{Master equation simulation with $T_{2}$ dissipation
    comparing the gates robust to $\delta \omega_{q}$ and $\delta A$ against
    the analytic gate.}
\end{figure}

%% TODO: Fig: Full ME simulation for best T1 and T\phi pulses
%% v.s. analytic

%% SECTION 6
\section{Discussion}
We have proposed some schemes and they work well.

@@

%% APPENDIX 3
\section{ME Simulation}
We model dissipation using the lindblad master
equation and standard collapse operators for
longitudinal relaxation and dephasing
of a two-level system.

>>>>

\documentclass[
  amsfonts,
  amsmath,
  tbtags,
  amssymb,
  aps,
  nobibnotes,
  %% prl,
  twocolumn,
]{revtex4-2}

@@

Some analytical methods
have been presented to address realistic experimental constraints.
Considering the dynamical and geometric phases of state
evolution has led to methods for achieving
robustness to pure dephasing in quantum systems
\cite{xu2020nonadiabatic, han2020experimental, merrill2014progress}.
Additionally, suitable choices of bases have been demonstrated that
allow the experimentalist to infer tradeoffs in longitudinal
and pure dephasing coherence times \cite{huang2020engineering}.
To date, however, no analytical method has been presented
to construct a gate while satisfying all relevant experimental
constraints. Furthermore, most analytic methods have only
been demonstrated in the two-level approximation and become
cumbersome to solve for larger Hilbert space sizes.

@@

(This work) We employ the trajectory optimization
literature to formulate the quantum
optimal control problem as a constrained optimization problem.
The trajectory optimization framework allows us to handle arbitrary
constraints on the evolution of the quantum state. Additionally,
we introduce methods for constructing gates robust to longitudinal
relaxation and pure dephasing, the dominant barriers to experimentally
realizing practical quantum computing.

We study the quantum optimal control problem on the fluxonium qubit.
We outline experimentally realistic constraints and map them to
the trajectory optimization framework. For the device we study
we achieve a 1.5x decrease in longitudinal relaxation probability.
We present two methods for achieving robustness to pure dephasing,
and compare them to existing dynamic decoupling methods. We find that 
our methods mitigate dephasing by order X over dynamic decoupling.

@@

%% SECTION 2
\section{QOC + AL-iLQR}
(QOC Problem Statement) Here we introduce the notation
we will use throughout the paper,
review the quantum optimal control problem statement,
and introduce the trajectory optimization framework.
Quantum optimal control concerns the evolution of
a quantum state $\ket{\psi(t)}$ governed by the time-dependent
Schroedinger equation (TDSE)
\label{eq:tdse}
\begin{align}
  \frac{d}{dt} \ket{\psi(t)} &= -\frac{i}{\hbar} H(u(t), t) \ket{\psi(t)}
\end{align}
The evolution is sometimes cast with the evolution
of a density matrix under the Lindblad master equation to
model the decoherence of the state explicitly. The Hamiltonian
has an arbitrary dependence on the possibly multi-valued controls $u(t)$.
The controls are so called because they are the means the experimentalist has to
act on the system.

Numerical quantum optimal control techniques make
the problem tractable by discretizing the problem into $N$
time steps. Typical integration techniques for the TDSE include
approximating unitary propagators as well as explicit integration methods,
such as Runge-Kutta, of the form
\label{eq:step-approx}
\begin{align}
  \ket{\psi_{k + 1}} \approx \ket{\psi_{k}} + \frac{d}{dt} \ket{\psi_{k}} \cdot \Delta t_{k}
\end{align}

Quantum optimal control seeks the control
parameters that minimize a functional $J(u(t))$.
In the simplest case the functional is
$J = 1 - {\lvert \braket{\psi_{f} \lvert \psi_{N}(u(t))} \rvert}^{2}$
the infidelity between the inital state evolved
to the final time step ($\ket{\psi_{N}(u(t))}$)
and the target state ($\ket{\psi_{f}}$). In general
$J$ is a linear combinaion of cost functions on the state, e.g.
forbidden-state occupation, as well as
cost functions on the controls, e.g. the norm of the control amplitudes
\cite{leung2017speedup}. Typical quantum optimal control
algorithms employ automatic differentiation
to compute first order information for the functional ($\nabla_{u} J(u)$).
They employ a first-order optimizer to minimize $J$ with respect to $u$.

(AL-iLQR Problem Statement) The trajectory optimization
literature solves a more general class of non-linear programs that resemble
the quantum optimal control problem. The quantum optimal control
problem is a specific case of the linear quadratic regulator (LQR).
LQR is so called because the dynamics are linear in the state and
the functional is quadratic in the state. In the LQR formulation
the same functional is evaluated at each time step
\begin{equation}
  J_{\textrm{iLQR}} = \tilde{x}_{N}^{T} Q_{N} \tilde{x}_{N}
  + \sum_{k = 0}^{N - 1} \tilde{x}_{k}^{T} Q_{k} \tilde{x}_{k} + u_{k}^{T} R_{k} u_{k}
\end{equation}
where $\tilde{x}_{k} = x_{k} - x_{f}$ is the difference between the state
at time step $k$ and final state, $u_{k}$ are the controls,
and $Q_{k}, R_{k}$ are matrices that define the penalty metric.
The state is propagated using a dynamics function similar to
equation \ref{eq:step-approx}
$x_{k + 1} = f(x_{k}, u_{k}, t_{k}, \Delta t_{k})$.
In the case of quantum optimal control $\ket{\psi_{k}} \subseteq x_{k}$
and $f$ encodes the TDSE dynamics.

@@

%% SECTION 3
\section{QOC on the Fluxonium}
(Fluxonium Device) In the following we study
the quantum optimal control problem on the fluxonium qubit.
In the two-level
approximation the system Hamiltonian takes the form
\label{eq:hamiltonian}
\begin{align}
  H/h &= \omega_{q} \frac{\sigma_{z}}{2} + a(t) \frac{\sigma_{x}}{2}
\end{align}
$h$ is Planck's constant. The flux amplitude $a$ is experimentally
realized by modulating the flux 
threading the deivce $\Phi_{\textrm{ext}}$.
The flux amplitude is obtained from the external flux by
$a = 4 \pi \braket{g \lvert \hat{\phi} \rvert e} \rvert_{0.5 \Phi_{0}} E_{L}
\delta \Phi_{\textrm{ext}} / (h \Phi_{0})$
where $\delta \Phi_{\textrm{ext}} = \Phi_{\textrm{ext}} - 0.5 \Phi_{0}$ is the flux
offset from the flux frustration point.

@@

(Constraints) We now outline the constraints that we require each gate
to obey.
We require $a(t = 0) = a(t = t_{N}) = 0$.
This constraint ensures gates may be concatenated arbitrarily without
inducing AWG ringing due to high-frequency transitions.
Furthermore, we require $\int_{0}^{t_{N}} a(t) dt = 0$. This
constraint ensures the pulse has zero net flux, mitigating
the hysteresis ubiquitous in flux bias lines.
%% TODO: See ref. 28 in Helin paper
We require $-300 \textrm{MHz} \le a(t) \le 300 \textrm{MHz}$
to ensure the two-level approximation \ref{eq:hamiltonian}
remains valid. Additionally, we require that each gate achieves
the desired state transition $\braket{\psi_{f} \lvert \psi_{N}} = 1$.
In addition to these constraints we penalize the norm
of the first and second derivatives of the control
to mitigate AWG ringing.

The optimization is performed
over the second derivative of the flux modulation amplitude
($\frac{d^{2}}{dt^{2}} a(t)$) so that the first derivative
($\frac{d}{dt} a(t)$), proportional ($a(t)$), and integral ($\int a(t)$)
are tracked in the augmented state vector $x$ and obtained by
integration in the dynamics function $f$.
Both the zero net flux and target quantum state constraint
are then handled by ensuring the augmented final state is
reached $x_{N} - x_{f} = 0$.
The equality and inequality constraints on $a(t)$ are handled
with a bound constraint.
%% TODO: probably want to list equations for the constraints

($T_{1}$ and $T_{\phi}$ noise)
In addition to optimizing the cost functional to achieve a gate
that obeys experimental constraints and has a high simulated fidelity,
we also want to make the gate robust to noise that affects the experimental
gate fidelity. Decoherence of the quantum state due to external noise
is typically modeled by two phenomena: longitudinal relaxation and pure dephasing.
They are modeled using their $1/e$ decay times $T_{1}$ and $T_{\phi}$ respectively
(see Appendix).
The main contributions to longitudinal relaxation in our
device are dielectric loss in the capacitor, resistive loss in the inductor,
and Purcell loss. The main contributions to pure dephasing in our
device are $1/f$ flux noise and decay via charge and flux coupling
to the control lines.

Dissipation to the thermal bath via longitudinal
relaxation is an irreversible process
that results in information loss.
Converesely, pure dephasing is a reversible process.
There is a tradeoff between the two decoherence processes. In the case of white
noise we have that the sum of the noise weights $W_{1}$ and $W_{\phi}$
is constant \cite{huang2020engineering}.
Our device achieves its best pure dephasing
protection at the flux frustration point
$T_{2e}(\Phi_{\textrm{ext}} = 0.5 \Phi_{0}) \sim 300 \mu\textrm{s}$
where the qubit frequency is first-order insensitive to changes in flux.
It becomes more succeptable to pure dephasing as the flux is tuned away from the flux
frustration point. Conversely, $T_{1}$ is at a minimum
at the flux frustration point $T_{1}(0.5 \Phi_{0}) = 0.315$ms,
and increases away from the flux frustration point
$T_{1}(0.43 \Phi_{0}) = 4.3$ms. Given the nature
of the decay processes and the tradeoff, we choose
to maximize the longitudinal relaxation time ($T_{1}$)
over the gate duration
and employ robust control techniques to mitigate
pure dephasing.
%% TODO: See fig. 3 in Helin paper

%% F4.1
%% TODO: Update images. Use new gates constructed with
%% spline T1 and use smaller sim times.
\begin{figure*}[!t]
  \begin{subfigure}{.3\linewidth}
    \includegraphics[width=\linewidth]{assets/00045_spin16.png}
    \label{fig:sub-first}
  \end{subfigure}
  \begin{subfigure}{.3\linewidth}
    \includegraphics[width=\linewidth]{assets/00047_spin16.png}
    \label{fig:sub-second}
  \end{subfigure}
  \begin{subfigure}{.3\linewidth}
    \includegraphics[width=\linewidth]{assets/00049_spin16.png}
    \label{fig:sub-third}
  \end{subfigure}
  \caption{Master equation simulation with $T_{1}$ dissipation for all basis gates.}
  \label{fig:fig}
\end{figure*}

%% SECTION 4
\section{Robustness to $T_{1}$-type Noise}
(Strategy) We seek to minimize the probability
that the qubit decays as a result of longitudinal
relaxation. To this end we augment the state vector ($x_{k}$) with the
longitudinal relaxation probability
\begin{equation}
  P_{1}(t_{k}) = \int_{0}^{t_{k}} \gamma_{1}(a(t)) dt
\end{equation}
where $\gamma_{1} = T_{1}^{-1}$. Setting the target
longitudinal relaxation probability to 0 results in
a quadratic cost at each knot point
of the form ${\lvert P_{1}(t_{k}) \rvert}^{2}$.

$\gamma_{1}(a_{k})$
is obtained at each knot point by evaluating
a spline interpolant fit to
experimentally obtained data of the form
$\{(\Phi_{\textrm{ext}}, T_{1})\}$.
$\Phi_{\textrm{ext}}$ is a function of $a_{k}$
with the inverse of the relation given in section 3.
Calculating $T_{1}$ directly from theoretical
considerations requires many high-dimensional
eigendecompositions, which
is computationally expensive. Additionally,
$T_{1}$ values are known to fluctuate greatly
with laboratory temperatures \cite{klimov2018fluctuations}.
Interpolating $T_{1}$ from experimental data increases
the fridge truth of the simulation.

@@

(Results) We achieve a factor of 1.5 decrease in the probability
of longitudinal relaxation from the analytic gates we benchmark
against. We simulate the performance of the gates using the
Lindblad master equation (see Appendix). We repeatedly apply the basis gates
and measure the fidelity of the resulting state as a function
of time as shown in Fig. 1.

%% T4.1
%% TODO: Update this table with spline T1 optimizations and calculations.
%% TODO: Maybe best for appendix.
%% TOOD: Maybe add some commentary about why we see more speedup
%% for Z/2 and X/2 than Y/2. In particular I think this is because of the
%% long idle times at the flux frustration point for Z/2 and X/2. It
%% might be a more fair comparison to show gates that have better T1s
%% and as good flux noise mitigation.
%% \begin{table}
%%   \begin{tabular}{c | c | c | c}
%%     & Analytic  & QOC &\\
%%     Gate & $P_{1}\ (10^{-5})$ & $P_{1}\ (10^{-5})$ & Speedup\\
%%     \hline
%%     Z/2 & 4.615 & 2.576 & 1.792\\
%%     Y/2 & 2.826 & 1.888 & 1.496\\
%%     X/2 & 9.562 & 5.080 & 1.882\\
%%   \end{tabular}
%%   \caption{Probability of longitudinal relaxation for each gate
%%     evaluated at the gate's duration.}
%% \end{table}

%% SECTION 5
\section{Robustness to $T_{\phi}$-type Noise}
(Strategy) For the fluxonium, pure dephasing acts
along the flux axis. Low frequency 1/$f$ noise,
Johnson-Nyquist current noise present in the flux bias
lines, and temperature dependent gain fluctuations
may cause the flux amplitude to deviate from its
desired value by an amount $\delta a$. Additionally,
residual calibration errors and fluctuations may cause
the qubit frequency to deviate from its measured value
by an amount $\delta \omega_{q}$.

System parameter
deviations are typically addressed with dynamic decoupling
sequences \cite{merrill2014progress},
the DRAG scheme \cite{krantz2019quantum}, or
geometric phase considerations
\cite{xu2020nonadiabatic} \cite{han2020experimental}.
Dynamic decoupling sequences compose rotations on the
Bloch sphere so that erroneous rotations arising due
to the parameter deviation are cancelled.
The latter two methods are inflexible. We draw on the
robust control literature to demonstrate
numerical techniques for engineering robustness
to parameter deviations.

We propose two methods for engineering robustness
to system parameter deviations. The first we call the
derivative method. We draw on the intuition that
making the state evolution insensitive to changes
in the system parameter is encoded in the derivative
$\partial_{\omega_{q}}^{l} \ket{\psi}$.
The $l$ state derviatives are added to the augmented
state vector. Their dynamics are found by differentiating
the TDSE dynamics with respect to the parameter of interest
\ref{eq:tdse}. Setting the target state derivatives
to zero vectors results in quadratic costs at each
knot point
${\lvert \partial_{\omega_{q}}^{l} \ket{\psi_{k}} \rvert}^{2}$.

The second scheme we analyze is the sampling method,
which is well studied in the robust control literature
\cite{manchester2016derivative} \cite{tronarp2016sigma}.
We augment the state vector with additional
states that follow deviant dynamics. The parameters of interest
are altered by a small deviation, typically chosen
to represent the distribution of the parameter.
For example, in the 3-point sampling method we
propagate $\ket{\psi_{\pm, I}}$ where
$\omega_{q}^{\pm} = \omega_{q} \pm \sigma_{\omega_{q}}$,
$\omega_{q}^{I} = \omega_{q}$.
The difference between the final states and the target
state is penalized, resulting in quadratic costs at
each knot point
${\lvert \ket{\psi_{\pm, I}} - \ket{\psi_{f}} \rvert}^{2}$

%% LOH

@@

%% F5.1
%% TODO: Update this and make sure it is for X/2.
%% I'm not sure if we should include all gates Z/2, Y/2, X/2
%% because I don't know what the dynamic decoupling analogy
%% for Z/2 and Y/2 are. On the other hand we would
%% want to include all of them to show that the benefit
%% is not uniform across gates.
%% (maybe add 5-sample and 3-derivative)
\begin{figure}
  %% \includegraphics[width=\linewidth]{assets/00005_spin12_hpsweep.png}
  \caption{fidelity v.s. $\omega$ for the $X/2$ gate via
    analytic, 3-sample, 2-derivative}
\end{figure}

%% F5.2
%% TODO: Update this and make sure it is for X/2.
%% Add inset to show high-performing variants at large time steps.
\begin{figure}
  %% \includegraphics[width=\linewidth]{assets/00006_spin12_hpsweep.png}
  \caption{fidelity at $\omega \pm \sigma_{\omega}$ v.s. time for the
    $X/2$ gate via analytic, 3-sample, 2-derivative}
\end{figure}

%% F5.3
%% TODO: Make this figure. My guess is we want a 5-sample, with 2 at \omega_{\pm}
%% and 2 at A_{\pm} as well as 2-derivative of both parameters separately.
%% (maybe add 5-sample and 3-derivative)
\begin{figure}
  %% \includegraphics[width=\linewidth]{assets/t2_temp.jpg}
  \caption{Master equation simulation with $T_{2}$ dissipation
    comparing the $X/2$ gate robust to $\delta \omega_{q}$ and $\delta a$ against
    the analytic gate.}
\end{figure}

%% TODO: Fig: Full ME simulation for best T1 and T\phi pulses
%% v.s. analytic (?)

%% SECTION 6
\section{Conclusion}
We have proposed some schemes and they work well.

@@

%% APPENDIX 3
\section{ME Simulation}
We model dissipation using the Lindblad master
equation and standard collapse operators for
longitudinal relaxation and dephasing
of a two-level system.
